Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Rewrite abstract.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
\documentclass{acm_proc_article-sp}
\usepackage{url}
%\usepackage{listings}

\begin{document}

@@

\numberofauthors{3}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
C. Scott Ananian\\
\affaddr{One Laptop Per Child Foundation}\\
\affaddr{222 Third Street}\\
\affaddr{Cambridge, MA 02142}\\
\email{cscott@laptop.org}
% 2nd. author
\alignauthor
Chris Ball\\
\affaddr{One Laptop Per Child Foundation}\\
\affaddr{222 Third Street}\\
\affaddr{Cambridge, MA 02142}\\
\email{cjb@laptop.org}
% 3rd. author
\alignauthor
Michael Stone\\
\affaddr{x}\\
% michael, fill in whatever affiliation you like here.
\email{mstone@laptop.org} % or other email address
%\and  % use '\and' if you need 'another row' of author names
}
\date{12 March 2012}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\begin{abstract}
Project Nell is tablet software to teach reading and writing to
children far from educational infrastructure.  Nell is a modular
narrative system with ``a low floor and no ceilings'': the design
scales from teaching letter shapes to programming the system itself.

Nell is the successor to the Sugar educational software developed by
One Laptop per Child for their XO-1 laptop.  Nell targets the XO-3
tablet, a sub-\$100 solar-powered tablet for the developing world.
%Experience with Sugar drove design choices for Nell.

\textbf{XXX REWRITE THE ABSTRACT XXX}
\end{abstract}

@@

We have not yet implemented an integrated story editor within Nell,
but we expect it to be roughly similar to the one implemented for
Wide Ruled, which showed good learnability by inexperienced
users~\cite{wideruled}.

@@

\subsection{Extensible dialog}
The child can interact with the Princess, and other agents within
Nell, directly.  Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult; even
the rudimentary conversational abilities of ELIZA elicited hours of
conversation~\cite{weizenbaum:power}.
% her secretary is divulging her life story
% asks him to leave the room so he could be alone with it
% hours discussing her boyfriend.
Nell's use as an interactive diary is enhanced by the child's
collaboration in the fiction that Nell is intelligent---what
Turkle~\cite{turkle:alone} calls the ``ELIZA effect.''

@@

The Sugar Learning environment~\cite{sugarXXX} is an earlier effort at
child education.  We've learned directly from this effort.  Nell
focuses on children even further from educational infrastructure.
The narrative at Nell's code attempts to provide students additional
pedagogical guidance, and the direct interaction model avoids keyboard
problems which have plagued Sugar's initial deployments.  Nell also
attempts to provide a greater sense of ownership through pervasive
customization.

>>>>

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%\documentclass{acm_proc_article-sp}
\documentclass[preprint]{sig-alternate}
\usepackage{url}
\usepackage{ifthen}\newboolean{noauthors}\setboolean{noauthors}{false}

\begin{document}\toappear{}

@@

\ifthenelse{\boolean{noauthors}}{}{
\numberofauthors{1}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
C. Scott Ananian \qquad Chris Ball \qquad Michael Stone\titlenote{%
Now at Akamai Technologies.}\\
\affaddr{One Laptop Per Child Foundation}\\
\affaddr{222 Third Street}\\
\affaddr{Cambridge, MA 02142}\\
\email{\{cscott,cjb,mstone\}@laptop.org}
%\and  % use '\and' if you need 'another row' of author names
}
}
\date{12 March 2012}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\begin{abstract}
% Draft 1
% Project Nell is tablet software to teach reading and writing to
% children far from educational infrastructure.  Nell is a modular
% narrative system with ``a low floor and no ceilings'': the design
% scales from teaching letter shapes to programming the system itself.
% Nell is the successor to the Sugar educational software developed by
% One Laptop per Child for their XO-1 laptop.  Nell targets the XO-3
% tablet, a sub-\$100 solar-powered tablet for the developing world.
% %Experience with Sugar drove design choices for Nell.

% Draft 2
% Motivated by ``lessons learned'' from five years of experience with our
% \textit{Sugar} education platform, we introduce \textit{Nell}: a Web- and
% tablet\footnote{Nell targets the XO-3 tablet, a sub-\$100 solar-powered tablet
% for the developing world.}-friendly education platform built around a novel
% modular narrative system designed to engage children far from educational
% infrastructure in their own personal pursuit of education and literacy.

% Draft 3
% We introduce \textit{Nell}: a Web- and tablet\footnote{Nell targets the XO-3
% tablet, a sub-\$100 solar-powered tablet for the developing world.}-friendly
% education platform built around a novel modular narrative system designed to
% engage children far from educational infrastructure in their own personal
% pursuit of education and literacy. Our design is informed and motivated by
% ``lessons learned'' from five years and $\sym2,000,000$ users' experience with
% our \textit{Sugar} education platform.

% Draft 4
% \textit{Nell} is a tablet-friendly\footnote{Nell's primary platform is the
% XO-3, an affordable solar-powered tablet for kids in the developing world.}
% education platform with a novel modular narrative system designed to engage
% children far from educational infrastructure in their own personal pursuit of
% literacy. Nell's design is informed by ``lessons learned'' from five years'
% experience with the first-generation \textit{Sugar} education platform,
% deployed to two million users.

% Draft 5
% \textit{Nell} is a tablet-friendly\footnote{Nell's primary platform is the
% XO-3, an affordable solar-powered tablet for kids in the developing world.}
% education platform with a novel modular narrative system designed to engage
% children in their own personal exploration of the world around them. Nell
% extends the design of the \textit{Sugar Learning
% Platform}\footnote{\url{http://sugarlabs.org}} to support new features
% requested by the field: \textit{user-editable scaffolding},
% \textit{personalized learning materials}, and \textit{improved authoring
% workflows}.

% Draft 6
\textit{Nell} is a tablet-friendly\footnote{Nell's primary platform is the
XO-3, an affordable solar-powered tablet for kids in the developing world.}
education platform with a novel modular narrative system designed to engage
children in their own personal pursuit of literacy. Nell extends the design of
the \textit{Sugar Learning Platform}\footnote{\url{http://sugarlabs.org}} to
better support \textit{narrative} and \textit{personalization} and to better
accommodate \textit{growth}, \textit{authoring}, and \textit{direct
interaction}.
\end{abstract}

@@

Nell's integrated story editor has not yet been implemented.  Its
design is patterned after the Wide Ruled authoring tool, which was
successfully used by non-technical story creators~\cite{skorupski:2009}.

@@

\subsection{Extensible dialog}
The child can directly interact with the Princess and other agents within
Nell.  Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult; even
the rudimentary conversational abilities of ELIZA elicited hours of
conversation~\cite{weizenbaum:power}.
% her secretary is divulging her life story
% asks him to leave the room so he could be alone with it
% hours discussing her boyfriend.
Nell's use as an interactive diary is enhanced by the child's
collaboration in the fiction that Nell is intelligent---what
Turkle~\cite{turkle:alone} calls the ``ELIZA effect.''

@@

The Sugar Learning Platform~\cite{sugar} is an earlier effort at
child education.  We've learned directly from this effort.  Nell
focuses on children even further from educational infrastructure.
The narrative at Nell's code attempts to provide students additional
pedagogical guidance, and the direct interaction model avoids keyboard
problems which have plagued Sugar's initial deployments.  Nell also
attempts to provide a greater sense of ownership through pervasive
customization.
